### 2014-02-05 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/abstract.tex
Latest submitted version

Feature selection is important in many practical supervised learning
settings to address computational constraints or to prevent
overfitting when the data may be high-dimensional but contain
relatively few samples.  While a wide variety of feature selection
methods have been proposed in the literature, little research seems to
focus on feature selection specifically targeted to improve recall in
the case of binary classification.  In this paper we propose a novel
probabilistic voting model of feature selection and argue that
choosing features so as to maximize likelihood objectives w.r.t. this
model provides an effective method for high recall feature selection.
For each objective, we derive an efficient formula for feature
selection in the filtering framework (i.e., greedy forward selection)
and we empirically compare the resulting feature selection criteria to
a wide variety of existing methods.  Results show that our high recall
feature selection approach does indeed improve recall with
improvements noticeable when there is a high feature to data ratio.
Such results provide a novel and efficient feature selection algorithm
to target high-recall classification tasks.

>>>>

Feature selection is important in many practical supervised learning
settings to address computational constraints or to prevent
overfitting when the data may be high-dimensional but contain
relatively few samples.  While a wide variety of feature selection
methods have been proposed in the literature, little research seems to
focus on feature selection specifically targeted to improve recall in
the case of binary classification.  In this paper we propose a novel
probabilistic voting model of feature selection and argue that
choosing features so as to maximize likelihood objectives w.r.t. this
model provides an effective method for high recall feature selection.
For each objective, we derive an efficient formula for feature
selection in the filtering framework (i.e., greedy forward selection)
and we empirically compare the resulting feature selection criteria to
a wide variety of existing methods.  Results show that our high recall
feature selection approach does indeed improve recall --- with
improvements most significant when there is a high feature to data ratio.
Such results provide a novel and efficient feature selection algorithm
to target high-recall classification tasks.

### 2014-02-05 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/conclusions.tex
Latest submitted version

In this paper we argued that no feature selection methods have
previously targeted recall for the task of binary classification and
we proposed a model and objectives to address this task.  Empirically,
our results show that our high recall feature selection approach shows
strong performance on recall with significant improvements over other
methods in cases where there is a high feature to data ratio.
Future extensions of this work may examine tighter integration of the
feature selection method with the algorithm to make an \emph{embedded}
approach 
using the classifier implicit in our model.
%based on our model since at it's core is a voting-based
%classifier.

>>>>

In this paper we argued that no feature selection methods have
previously targeted recall for the task of binary classification and
we proposed a model and objectives to address this task.  Empirically,
our results show that our high recall feature selection approach shows
strong performance on recall with significant improvements over other
methods in cases where there is a high feature to data ratio.
Future work may examine tighter integration of our 
feature selection method with its implicit classification 
algorithm in an efficient embedded approach to high-recall feature selection.
%using the classifier implicit in our model.
%based on our model since at it's core is a voting-based
%classifier.

### 2014-02-05 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/related_work.tex
Latest submitted version

Although existing algorithms give various solutions, they are mostly
ad-hoc, until \cite{brown2012conditional}. Brown et al.\ derived a 
probabilistic model with information-theoretic motivations from first principles, and retro-fitted
existing information-theory-based feature selection methods to the
model. In this paper, we also take a derivational approach to
specifying a probabilistic model and optimizing a feature selection
objective w.r.t. that model, but in our case we focus on the specific
task of optimizing for recall in binary classification, which it 
seems no prior method has focused on in previous work.

>>>>

While most existing feature selection methods provide heuristic
motivation,   \citeauthor{brown2012conditional} 
\shortcite{brown2012conditional} derived a
probabilistic model with information-theoretic motivations from first
principles, and retro-fitted existing information-theory-based feature
selection methods to their model.

In this paper, we take a derivational approach similar to \citeauthor{brown2012conditional} 
\shortcite{brown2012conditional}
that specifies a probabilistic model and optimizes a feature selection
objective w.r.t. that model, but in our case we focus on the specific
task of optimizing for recall in binary classification, which it 
seems no prior method has focused on in previous work.  We present
our model and derivation next.
